\subsection{Background in Benchmarking}
There are many cases in the industry, in research and in education where benchmarking of
a software product is important. In industry benchmarks can be used to ensure that software
performance is acceptable. In the competitive commercial world, benchmarks can serve to inform
buyers of comparative performance of competing products. The benchmarking forms an integral
part of research related to the development of new algorithms and techniques as well as the refinement
and optimization of existing operations. Algorithm and data structure benchmarks can be applied
as a very useful teaching tool for students to review the notions of space and time complexity.
\\
\\
It is strange that although benchmarking seem to be a very common and useful application, very few benchmarking tools or services are available. Those that are available requires intricate configuration that may be beyond the reach of the developers, researchers,
teachers and students who would like to use them. The development of a benchmarking service which can be used in a generic way would therefore be welcomed by a large
potential user base.
\\
\\
\subsection{Our System}
Our system will consist of \textbf{Five} Modules namely User Managment, Benchmarking Service, Reporting, Notifications and Test Data.\\
The following modules may contain, and are not limited to the follwing, as according to Agile Process.

\subsubsection{User Managment}
This module consists of:
\begin{itemize}
  \item User Admin
  \item User Signup
  \item User Login
  \item User Profile Managment
\end{itemize}

\subsubsection{Benchmarking Service}
This module consists of:
\begin{itemize}
  \item Backend to run the user program
  \item Watcher service to monitor the program.
\end{itemize}

\subsubsection{Reporting}
This module consists of:
\begin{itemize}
  \item Reporting of a Benchmarking instance
  \item Comparing multiple Benchmakrs
  \item Exporting to report pdf
\end{itemize}

\subsubsection{Notifications}
This module consists of:
\begin{itemize}
  \item Notifying the user that there Benchmark is complete
\end{itemize}

\subsubsection{Test Data}
This module consists of:
\begin{itemize}
  \item Providing basic template data
  \item Adding data to repository
  \item Generating Test data
  \item Storing Test Data
\end{itemize}
