
\subsection{Architecture Requirements}
This section will discuss the architectural requirements of the containment
system in place.

\subsubsection{Quality Requirements}
The sections below will discuss the quality requirements the containment 
system will need to adhere to.
\paragraph{Flexibility}
The container needs to be able to handle multiple types of programs to benchmark
as well as being language agnostic. 

\paragraph{Maintainability}
The container environment should be self-maintaining after the initial setup of
the container, there should be no need for an administrator to maintain the container
environment.

\paragraph{Scalability}
Each container environment will only be running one program at a time.

\paragraph{Performance}
The use of a container in the system should impact performance negligibly, while
it will separate the program being tested from the system we hope that this will
not impact the performance of the benchmarking.  


\paragraph{Reliability}
The implementation of the container has the aim of increasing the reliability of
the system as a whole. This is because the container will separate the program
being benchmarked from the system as a whole and will nullify any malicious 
program from making changes to the system.

\subsubsection{Architectural Responsibilities}
The current responsibilities of the container environment are to separate the
testing environment from the system. 

\subsubsection{Architecture Constraints}
The chosen technology should be an accepted standard as well as being sufficiently
documented and supported

\subsection{Architecture Design}
\subsubsection{Tactics}

\subsubsection{Architectural Components}

\subsubsection{Frameworks and Technologies}
To implement the container environment we have decided to use \textbf{Docker} as
this containment environment is well tested, well documented, with wide support.
Docker is initialized from the start which is why it surpassed our other consideration
of using the native \textbf{Linux Containment} system, as this would require setup
needing in depth knowledge of a system we weren't comfortable with.

\paragraph{Concepts and Constraints for Application Components}
